Prefetching SPARQL query cacher

### 2016-05-31 dissertation/related.tex
start of query planner description

>>>>

The query planner first examines all connected subgraphs of a full
SPARQL query, and generates canonical labels for each one. Since it
insists on caching connected subgraphs, it avoids the problem I
encountered in Chapter~\ref{sec:tpfcacheplanning} that the cache may
break up connected subgraphs and thus create Cartesian joins.
